tabla_mean_values Mhuber

### 2017-09-15 analysis/tables_resiliences.Rmd
update tablas

---
title: "tabla_mean_values Mhuber"
author: "AJ Perez-Luque (@ajpelu)"
date: "2017"
output:  
  md_document:
    variant: markdown_github
bibliography: ../references.bib 
csl: ../ecology.csl
---

@@

### Tablas Disturb year  
```{r}
evi_a <- mhuber_eviA %>% 
  mutate(M.Huber = round(M.Huber, 4),
         lower.ci = round(lower.ci, 4),
         upper.ci = round(upper.ci, 4)) %>% 
  unite("ci", c("lower.ci", "upper.ci"), sep=", ") %>% 
  mutate(ci = paste0('(', ci, ')')) %>% 
  unite("value_EVI", c("M.Huber", "ci"), sep= " ") %>%
  dplyr::select(-MonoLetter, -n) %>% 
  dplyr::select(var, disturb_year, value_EVI, letter_EVI=Letter) %>% as.data.frame()

@@

mhuberA %>% pander()

mhuberA

# Tablas site
```{r}
evi_b <- mhuber_eviB %>% 
  mutate(M.Huber = round(M.Huber, 4),
         lower.ci = round(lower.ci, 4),
         upper.ci = round(upper.ci, 4)) %>% 
  unite("ci", c("lower.ci", "upper.ci"), sep=", ") %>% 
  mutate(ci = paste0('(', ci, ')')) %>% 
  unite("value_EVI", c("M.Huber", "ci"), sep= " ") %>%
  dplyr::select(-MonoLetter, -n) %>% 
  dplyr::select(var, site, value_EVI, letter_EVI=Letter) %>% as.data.frame()

@@

# Tablas Interaction
```{r}
evi <- mhuber_evi %>% 
  mutate(M.Huber = round(M.Huber, 4),
         lower.ci = round(lower.ci, 4),
         upper.ci = round(upper.ci, 4)) %>% 
  unite("ci", c("lower.ci", "upper.ci"), sep=", ") %>% 
  mutate(ci = paste0('(', ci, ')')) %>% 
  unite("value_EVI", c("M.Huber", "ci"), sep= " ") %>%
  dplyr::select(-MonoLetter, -n) %>% 
  dplyr::select(var,  disturb_year, site, value_EVI, letter_EVI=Letter) %>% as.data.frame()

>>>>

---
title: "tabla_mean_values Mhuber"
author: "AJ Perez-Luque (@ajpelu)"
date: "2017"
output: pdf_document
bibliography: ../references.bib 
csl: ../ecology.csl
---

@@

## Tablas Disturb year  
```{r, echo=FALSE}
evi_a <- mhuber_eviA %>% 
  mutate(M.Huber = round(M.Huber, 4),
         lower.ci = round(lower.ci, 4),
         upper.ci = round(upper.ci, 4)) %>% 
  unite("ci", c("lower.ci", "upper.ci"), sep=", ") %>% 
  mutate(ci = paste0('(', ci, ')')) %>% 
  unite("value_EVI", c("M.Huber", "ci"), sep= " ") %>%
  dplyr::select(-MonoLetter, -n) %>% 
  dplyr::select(var, disturb_year, value_EVI, letter_EVI=Letter) %>% as.data.frame()

@@

mhuberA %>% pander() 
```

## Tablas site
```{r, echo=FALSE}
evi_b <- mhuber_eviB %>% 
  mutate(M.Huber = round(M.Huber, 4),
         lower.ci = round(lower.ci, 4),
         upper.ci = round(upper.ci, 4)) %>% 
  unite("ci", c("lower.ci", "upper.ci"), sep=", ") %>% 
  mutate(ci = paste0('(', ci, ')')) %>% 
  unite("value_EVI", c("M.Huber", "ci"), sep= " ") %>%
  dplyr::select(-MonoLetter, -n) %>% 
  dplyr::select(var, site, value_EVI, letter_EVI=Letter) %>% as.data.frame()

@@

## Tablas Interaction
```{r, echo=FALSE}
evi <- mhuber_evi %>% 
  mutate(M.Huber = round(M.Huber, 4),
         lower.ci = round(lower.ci, 4),
         upper.ci = round(upper.ci, 4)) %>% 
  unite("ci", c("lower.ci", "upper.ci"), sep=", ") %>% 
  mutate(ci = paste0('(', ci, ')')) %>% 
  unite("value_EVI", c("M.Huber", "ci"), sep= " ") %>%
  dplyr::select(-MonoLetter, -n) %>% 
  dplyr::select(var,  disturb_year, site, value_EVI, letter_EVI=Letter) %>% as.data.frame()
